models with mice

### 2024-03-07 withmice.Rmd
comparing imputed and original data for ecopol scale via boxplots

## Mifa dor Kahan scale 
```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

@@

```{r}
orgscores <- data.frame(kahanefascores)

@@

summary(complete_ecopol_5)
```

>>>>

## Mifa for Kahan scale 
```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

@@

@@

summary(complete_ecopol_5)

nscores <- data.frame(ecopolall_scores$scores)
nscores

# Add an identifier column to each dataset
fct_scores2$Dataset <- 'imputed'
nscores$Dataset <- 'original'

# Combine the datasets for plotting
compare2 <- rbind(fct_scores2, nscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
compare2<- compare2[, c("MR1", "MR2", "Dataset")]

ggplot(compare2, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Pdevelop for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

ggplot(compare2, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Ndevelop for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()
